# Data Cleaning and EDA

```{r}
#| label: load functions and data
#| echo: false
source(file = "functions/stats.R")
source(file = "functions/plots.R")

ames <- read_rds(file = "data/ames-renamed.RDS")
```

::: {.callout-note appearance="simple"}
## Main Findings

TO DO
:::

## id

Unique observation ID.

## pid

Parcel identification number - can be used with city web site for parcel review.

## ms_sub_class

Nominal Variable.

Identifies the type of dwelling involved in the sale.

```{r}
#| label: ms_sub_class reconding
#| code-fold: true
ames <- ames  |> 
    
    mutate(
        ms_sub_class =
            recode_factor(
                
                factor(ms_sub_class),
                
                "020" = "One_Story_1946_and_Newer_All_Styles",
                "030" = "One_Story_1945_and_Older",
                "040" = "One_Story_with_Finished_Attic_All_Ages",
                "045" = "One_and_Half_Story_Unfinished_All_Ages",
                "050" = "One_and_Half_Story_Finished_All_Ages",
                "060" = "Two_Story_1946_and_Newer",
                "070" = "Two_Story_1945_and_Older",
                "075" = "Two_and_Half_Story_All_Ages",
                "080" = "Split_or_Multilevel",
                "085" = "Split_Foyer",
                "090" = "Duplex_All_Styles_and_Ages",
                "120" = "One_Story_PUD_1946_and_Newer",
                "150" = "One_and_Half_Story_PUD_All_Ages",
                "160" = "Two_Story_PUD_1946_and_Newer",
                "180" = "PUD_Multilevel_Split_Level_Foyer",
                "190" = "Two_Family_Conversion_All_Styles_and_Ages"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: ms_sub_class frequency table
#| echo: false
ames |> 
    nominal_frequency_table(ms_sub_class)
```

## Frequency Plot

```{r}
#| label: ms_sub_class frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(ms_sub_class,
                          nominal_label = "MS Sub Class",
                          title         = "Ms Sub Class Distribution")
```

## Relationship with Target Variable

```{r}
#| label: ms_sub_class vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = ms_sub_class,
                        nominal_label = "MS Sub Class",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "MS Sub Class vs Sale Price")
```

:::

## ms_zoning

Nominal Variable.

Identifies the general zoning classification of the sale.

```{r}
#| label: ms_zoning reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        ms_zoning =
            recode_factor(
                
                factor(ms_zoning),
                
                "A (agr)" = "Agriculture",
                "C (all)" = "Commercial",
                "FV"      = "Floating_Village_Residential",
                "I (all)" = "Industrial",
                "RH"      = "Residential_High_Density",
                "RL"      = "Residential_Low_Density",
                "RM"      = "Residential_Medium_Density"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: ms_zoning frequency table
#| echo: false
ames |> 
    nominal_frequency_table(ms_zoning)
```

## Frequency Plot

```{r}
#| label: ms_zoning frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(ms_zoning,
                          nominal_label = "MS Zoning",
                          title         = "Ms Zoning Distribution")
```

## Relationship with Target Variable

```{r}
#| label: ms_zoning vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = ms_zoning,
                        nominal_label = "MS Zoning",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "MS Zoning vs Sale Price")
```

:::

## lot_frontage

Numeric Variable.

Linear feet of street connected to property.

::: {.panel-tabset}

## Missing Values

```{r}
#| label: lot_frontage missing values
ames |> 
    summarise(NAs = sum(is.na(lot_frontage)))
```

When values are missing we assume that the value is zero.

```{r}
#| label: lot_frontage impute
#| code-fold: true
ames <- ames |> 
    mutate(lot_frontage = replace_na(lot_frontage, 0))
```

## Distribution

```{r}
#| label: lot_frontage distribution
#| echo: false
ames |> 
    numeric_distribution(lot_frontage,
                         xlabel = "Lot Frontage (ft)",
                         title  = "Lot Frontage Distribution")
```

## Summary Statistics

```{r}
#| label: lot_frontage summary statistics
#| echo: false
ames |>
    numeric_summary_table(lot_frontage)
```

## Relationship with Target Variable

```{r}
#| label: lot_frontage vs sale_price
#| echo: false
ames |>
    scatter_plot(x_numeric = lot_frontage, y_numeric = sale_price,
                 "Lot Frontage (ft)", "Sale Price ($)",
                 "Sale Price vs Lot Frontage")
```

:::

## lot_area

Numeric Variable.

Lot size in square feet.

::: {.panel-tabset}

## Missing Values

```{r}
#| label: lot_area missing values
ames |> 
    summarise(NAs = sum(is.na(lot_area)))
```

## Distribution

```{r}
#| label: lot_area distribution
#| echo: false
ames |> 
    numeric_distribution(lot_area,
                         xlabel = "Lot Area (ft2)",
                         title  = "Lot Area Distribution")
```

## Summary Statistics

```{r}
#| label: lot_area summary statistics
#| echo: false
ames |>
    numeric_summary_table(lot_area)
```

## Relationship with Target Variable

```{r}
#| label: lot_area vs sale_price
#| echo: false
ames |>
    scatter_plot(x_numeric = lot_area,
                 y_numeric = sale_price,
                 "Lot Area (ft2)", "Sale Price ($)",
                 "Sale Price vs Lot Area")
```

:::

## street

Nominal Variable.

Type of road access to property.

```{r}
#| label: street reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        street =
            recode_factor(
                
                factor(street),
                
                "Grvl" = "Gravel",
                "Pave" = "Paved"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: street frequency table
#| echo: false
ames |> 
    nominal_frequency_table(street)
```

## Frequency Plot

```{r}
#| label: street frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(street,
                          nominal_label = "Street",
                          title         = "Street Distribution")
```

## Relationship with Target Variable

```{r}
#| label: street vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = street,
                        nominal_label = "Street",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Street vs Sale Price")
```

:::

## alley

Nominal Variable.

Type of alley access to property.

::: {.panel-tabset}

## Missing Values

```{r}
#| label: alley missing values
ames |> 
    summarise(NAs = sum(is.na(alley)))
```

Missing values are coded as `"No Alley Access"`.

```{r}
#| label: alley reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        alley = replace_na(alley, "No Alley Access"),
        
        alley = recode_factor(
            
            factor(alley),
            
            "Grvl"            = "Gravel",
            "Pave"            = "Paved",
            "No Alley Access" = "No Alley Access"
        )
    )
```

## Frequency Table

```{r}
#| label: alley frequency table
#| echo: false
ames |> 
    nominal_frequency_table(alley)
```

## Frequency Plot

```{r}
#| label: alley frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(alley,
                          nominal_label = "Alley",
                          title         = "Alley Distribution")
```

## Relationship with Target Variable

```{r}
#| label: alley vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = alley,
                        nominal_label = "Alley",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Alley vs Sale Price")
```

:::

## lot_shape

Nominal Variable.

General shape of property.

```{r}
#| label: lot_shape reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        lot_shape =
            recode_factor(
                
                factor(lot_shape),
                
                "IR3" = "Irregular",
                "IR2" = "Moderately Irregular",
                "IR1" = "Slightly Irregular",
                "Reg" = "Regular"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: lot_shape frequency table
#| echo: false
ames |> 
    nominal_frequency_table(lot_shape)
```

## Frequency Plot

```{r}
#| label: lot_shape frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(lot_shape,
                          nominal_label = "Lot Shape",
                          title         = "Lot Shape Distribution")
```

## Relationship with Target Variable

```{r}
#| label: lot_shape vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = lot_shape,
                        nominal_label = "Lot Shape",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Lot Shape vs Sale Price")
```

:::

## land_contour

Nominal Variable.

Flatness of the property.

```{r}
#| label: land_contour reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        land_contour =
            recode_factor(
                
                factor(land_contour),
                
                "Lvl" = "Near Flat Level",
                "Bnk" = "Banked",
                "HLS" = "Hillside",
                "Low" = "Depression"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: land_contour frequency table
#| echo: false
ames |> 
    nominal_frequency_table(land_contour)
```

## Frequency Plot

```{r}
#| label: land_contour frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(land_contour,
                          nominal_label = "Land Contour",
                          title         = "Land Contour Distribution")
```

## Relationship with Target Variable

```{r}
#| label: land_contour vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = land_contour,
                        nominal_label = "Land Contour",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Land Contour vs Sale Price")
```

:::

## utilities

Nominal Variable.

Type of utilities available.

```{r}
#| label: utilities reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        utilities =
            recode_factor(
                
                factor(utilities),
                
                "NoSeWa" = "Electricity Gas",
                "NoSewr" = "Electricity Gas Water",
                "AllPub" = "All Public Utilities"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: utilities frequency table
#| echo: false
ames |> 
    nominal_frequency_table(utilities)
```

## Frequency Plot

```{r}
#| label: utilities frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(utilities,
                          nominal_label = "Utilities",
                          title         = "Utilities Distribution")
```

## Relationship with Target Variable

```{r}
#| label: utilities vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = utilities,
                        nominal_label = "Utilities",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Utilities vs Sale Price")
```

:::

## lot_configuration

Nominal Variable.

Lot configuration.

```{r}
#| label: lot_configuration reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        lot_configuration =
            recode_factor(
                
                factor(lot_configuration),
                
                "Inside"  = "Inside Lot",
                "Corner"  = "Corner Lot",
                "CulDSac" = "Cul de Sac",
                "FR2"     = "Frontage on 2 Sides",
                "FR3"     = "Frontage on 3 Sides"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: lot_configuration frequency table
#| echo: false
ames |> 
    nominal_frequency_table(lot_configuration)
```

## Frequency Plot

```{r}
#| label: lot_configuration frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(lot_configuration,
                          nominal_label = "Lot Configuration",
                          title         = "Lot Configuration Distribution")
```

## Relationship with Target Variable

```{r}
#| label: lot_configuration vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = lot_configuration,
                        nominal_label = "Lot Configuration",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Lot Configuration vs Sale Price")
```

:::

## land_slope

Nominal Variable.

Slope of property.

```{r}
#| label: land_slope reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        land_slope =
            recode_factor(
                
                factor(land_slope),
                
                "Gtl" = "Gentle Slope",
                "Mod" = "Moderate Slope",
                "Sev" = "Severe Slope"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: land_slope frequency table
#| echo: false
ames |> 
    nominal_frequency_table(land_slope)
```

## Frequency Plot

```{r}
#| label: land_slope frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(land_slope,
                          nominal_label = "Land Slope",
                          title         = "Land Slope Distribution")
```

## Relationship with Target Variable

```{r}
#| label: land_slope vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = land_slope,
                        nominal_label = "Land Slope",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Land Slope vs Sale Price")
```

:::

## neighborhood

Nominal Variable.

Physical locations within Ames city limits.

```{r}
#| label: neighborhood reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        neighborhood =
            recode_factor(
                
                factor(neighborhood),
                
                "Blmngtn"     = "Bloomington Heights",
                "Blueste"     = "Bluestem",
                "BrDale"      = "Briardale",
                "BrkSide"     = "Brookside",
                "ClearCr"     = "Clear Creek",
                "CollgCr"     = "College Creek",
                "Crawfor"     = "Crawford",
                "Edwards"     = "Edwards",
                "Gilbert"     = "Gilbert",
                "Greens"      = "Greens",
                "GrnHill"     = "Green Hills",
                "IDOTRR"      = "Iowa DOT and Rail Road",
                "Landmrk"     = "Landmark",
                "MeadowV"     = "Meadow Village",
                "Mitchel"     = "Mitchell",
                "NAmes"       = "North Ames",
                "NoRidge"     = "Northridge",
                "NPkVill"     = "Northpark Villa",
                "NridgHt"     = "Northridge Heights",
                "NWAmes"      = "Northwest Ames",
                "OldTown"     = "Old Town",
                "SWISU"       = "South and West of Iowa State University",
                "Sawyer"      = "Sawyer",
                "SawyerW"     = "Sawyer West",
                "Somerst"     = "Somerset",
                "StoneBr"     = "Stone Brook",
                "Timber"      = "Timberland",
                "Veenker"     = "Veenker",
                "Hayden Lake" = "Hayden Lake"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: neighborhood frequency table
#| echo: false
ames |> 
    nominal_frequency_table(neighborhood)
```

## Frequency Plot

```{r}
#| label: neighborhood frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(neighborhood,
                          nominal_label = "Neighborhood",
                          title         = "Neighborhood Distribution")
```

## Relationship with Target Variable

```{r}
#| label: neighborhood vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = neighborhood,
                        nominal_label = "Neighborhood",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Neighborhood vs Sale Price")
```

:::

## condition_1

Nominal Variable.

Proximity to various conditions.

```{r}
#| label: condition_1 reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        condition_1 =
            recode_factor(
                
                factor(condition_1),
                
                "Artery" = "Adjacent Arterial Street",
                "Feedr"  = "Adjacent Feeder Street",
                "Norm"   = "Normal",
                "RRNn"   = "Within 200 North South Railroad",
                "RRAn"   = "Adjacent North South Railroad",
                "PosN"   = "Near Positive off Site Feature",
                "PosA"   = "Adjacent Postive off Site Feature",
                "RRNe"   = "Within 200 East West Railroad",
                "RRAe"   = "Adjacent East West Railroad"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: condition_1 frequency table
#| echo: false
ames |> 
    nominal_frequency_table(condition_1)
```

## Frequency Plot

```{r}
#| label: condition_1 frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(condition_1,
                          nominal_label = "Condition 1",
                          title         = "Condition 1 Distribution")
```

## Relationship with Target Variable

```{r}
#| label: condition_1 vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = condition_1,
                        nominal_label = "Condition 1",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Condition 1 vs Sale Price")
```

:::

## condition_2

Nominal Variable.

Proximity to various conditions (if more than one is present).

```{r}
#| label: condition_2 reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        condition_2 =
            recode_factor(
                
                factor(condition_2),
                
                "Artery" = "Adjacent Arterial Street",
                "Feedr"  = "Adjacent Feeder Street",
                "Norm"   = "Normal",
                "RRNn"   = "Within 200 North South Railroad",
                "RRAn"   = "Adjacent North South Railroad",
                "PosN"   = "Near Positive off Site Feature",
                "PosA"   = "Adjacent Postive off Site Feature",
                "RRNe"   = "Within 200 East West Railroad",
                "RRAe"   = "Adjacent East West Railroad"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: condition_2 frequency table
#| echo: false
ames |> 
    nominal_frequency_table(condition_2)
```

## Frequency Plot

```{r}
#| label: condition_2 frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(condition_2,
                          nominal_label = "Condition 2",
                          title         = "Condition 2 Distribution")
```

## Relationship with Target Variable

```{r}
#| label: condition_2 vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = condition_2,
                        nominal_label = "Condition 2",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Condition 2 vs Sale Price")
```

:::

## building_type

Nominal Variable.

Type of dwelling.

```{r}
#| label: building_type reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        building_type =
            recode_factor(
                
                factor(building_type),
                
                "1Fam"   = "One Family Detached",
                "2fmCon" = "Two Family Conversion",
                "Duplx"  = "Duplex",
                "TwnhsE" = "Townhouse End Unit",
                "Twnhs"  = "Townhouse Inside Unit"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: building_type frequency table
#| echo: false
ames |> 
    nominal_frequency_table(building_type)
```

## Frequency Plot

```{r}
#| label: building_type frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(building_type,
                          nominal_label = "Building Type",
                          title         = "Building Type Distribution")
```

## Relationship with Target Variable

```{r}
#| label: building_type vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = building_type,
                        nominal_label = "Building Type",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Building Type vs Sale Price")
```

:::

## house_style

Nominal Variable.

Style of dwelling.

```{r}
#| label: house_style reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        house_style =
            recode_factor(
                
                factor(house_style),
                
                "1Story" = "One Story",
                "1.5Fin" = "One and Half Story 2nd Level Finished",
                "1.5Unf" = "One and Half Story 2nd Level Unfinished",
                "2Story" = "Two Story",
                "2.5Fin" = "Two and Half Story 2nd Level Finished",
                "2.5Unf" = "Two and Half Story 2nd Level Unfinished",
                "SFoyer" = "Split Foyer",
                "SLvl"   = "Split Level"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: house_style frequency table
#| echo: false
ames |> 
    nominal_frequency_table(house_style)
```

## Frequency Plot

```{r}
#| label: house_style frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(house_style,
                          nominal_label = "House Style",
                          title         = "House Style Distribution")
```

## Relationship with Target Variable

```{r}
#| label: house_style vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = house_style,
                        nominal_label = "House Style",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "House Style vs Sale Price")
```

:::

## overall_quality

Nominal Variable.

Rates the overall material and finish of the house.

```{r}
#| label: overall_quality reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(overall_quality = factor(overall_quality))
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: overall_quality frequency table
#| echo: false
ames |> 
    nominal_frequency_table(overall_quality)
```

## Frequency Plot

```{r}
#| label: overall_quality frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(overall_quality,
                          nominal_label = "Overall Quality",
                          title         = "Overall Quality Distribution")
```

## Relationship with Target Variable

```{r}
#| label: overall_quality vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = overall_quality,
                        nominal_label = "Overall Quality",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Overall Quality vs Sale Price")
```

:::

## overall_condition

Nominal Variable.

Rates the overall material and finish of the house.

```{r}
#| label: overall_condition reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(overall_condition = factor(overall_condition))
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: overall_condition frequency table
#| echo: false
ames |> 
    nominal_frequency_table(overall_condition)
```

## Frequency Plot

```{r}
#| label: overall_condition frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(overall_condition,
                          nominal_label = "Overall Condition",
                          title         = "Overall Condition Distribution")
```

## Relationship with Target Variable

```{r}
#| label: overall_condition vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = overall_quality,
                        nominal_label = "Overall Condition",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Overall Condition vs Sale Price")
```

:::

## year_built

Original construction date.

```{r}
#| label: year_built frequency table
#| echo: false
# ames |> 
#     nominal_frequency_table(year_built)
```

## year_remod_add

Remodel date (same as construction date if no remodeling or additions).

```{r}
#| label: year_remod_add frequency table
#| echo: false
# ames |> 
#     nominal_frequency_table(year_remod_add)
```

## roof_style

Nominal Variable.

Type of roof.

```{r}
#| label: roof_style reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        roof_style =
            recode_factor(
                
                factor(roof_style),
                
                "Flat"    = "Flat",
                "Gable"   = "Gable",
                "Gambrel" = "Gabrel Barn",
                "Hip"     = "Hip",
                "Mansard" = "Mansard",
                "Shed"    = "Shed"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: roof_style frequency table
#| echo: false
ames |> 
    nominal_frequency_table(roof_style)
```

## Frequency Plot

```{r}
#| label: roof_style frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(roof_style,
                          nominal_label = "Roof Style",
                          title         = "Roof Style Distribution")
```

## Relationship with Target Variable

```{r}
#| label: roof_style vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = roof_style,
                        nominal_label = "Roof Style",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Roof Style vs Sale Price")
```

:::

## roof_material

Nominal Variable.

Roof material.

```{r}
#| label: roof_material reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        roof_material =
            recode_factor(
                
                factor(roof_material),
                
                "ClyTile" = "Clay or Tile",
                "CompShg" = "Composite Shingle",
                "Membran" = "Membrane",
                "Metal"   = "Metal",
                "Roll"    = "Roll",
                "Tar&Grv" = "Gravel and Tar",
                "WdShake" = "Wood Shakes",
                "WdShngl" = "Wood Shingles"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: roof_material frequency table
#| echo: false
ames |> 
    nominal_frequency_table(roof_material)
```

## Frequency Plot

```{r}
#| label: roof_material frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(roof_material,
                          nominal_label = "Roof Material",
                          title         = "Roof Material Distribution")
```

## Relationship with Target Variable

```{r}
#| label: roof_material vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = roof_material,
                        nominal_label = "Roof Material",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Roof Style vs Sale Price")
```

:::

## exterior_1st

Nominal Variable.

Exterior covering on house.

```{r}
#| label: exterior_1st reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        exterior_1st =
            recode_factor(
                
                factor(exterior_1st),
                
                "AsbShng" = "Asbestos Shingles",
                "AsphShn" = "Asphalt Shingles",
                "BrkComm" = "Brick Common",
                "BrkFace" = "Brick Face",
                "CBlock"  = "Cinder Block",
                "CemntBd" = "Cement Board",
                "HdBoard" = "Hard Board",
                "ImStucc" = "Imitation Stucco",
                "MetalSd" = "Metal Siding",
                "Other"   = "Other",
                "Plywood" = "Plywood",
                "PreCast" = "PreCast",
                "Stone"   = "Stone",
                "Stucco"  = "Stucco",
                "VinylSd" = "Vinyl Siding",
                "Wd Sdng" = "Wood Siding",
                "WdShing" = "Wood Shingles"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: exterior_1st frequency table
#| echo: false
ames |> 
    nominal_frequency_table(exterior_1st)
```

## Frequency Plot

```{r}
#| label: exterior_1st frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(exterior_1st,
                          nominal_label = "Exterior 1st",
                          title         = "Exterior 1st Distribution")
```

## Relationship with Target Variable

```{r}
#| label: exterior_1st vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = exterior_1st,
                        nominal_label = "Exterior 1st",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Exterior 1st vs Sale Price")
```

:::

## exterior_2nd

Nominal Variable.

Exterior covering on house (if more than one material).

```{r}
#| label: exterior_2nd reconding
#| code-fold: true
ames <- ames |> 
    
    mutate(
        exterior_2nd =
            recode_factor(
                
                factor(exterior_2nd),
                
                "AsbShng" = "Asbestos Shingles",
                "AsphShn" = "Asphalt Shingles",
                "Brk Cmn" = "Brick Common",
                "BrkFace" = "Brick Face",
                "CBlock"  = "Cinder Block",
                "CmentBd" = "Cement Board",
                "HdBoard" = "Hard Board",
                "ImStucc" = "Imitation Stucco",
                "MetalSd" = "Metal Siding",
                "Other"   = "Other",
                "Plywood" = "Plywood",
                "PreCast" = "PreCast",
                "Stone"   = "Stone",
                "Stucco"  = "Stucco",
                "VinylSd" = "Vinyl Siding",
                "Wd Sdng" = "Wood Siding",
                "Wd Shng" = "Wood Shingles"
            )
    )
```

::: {.panel-tabset}

## Frequency Table

```{r}
#| label: exterior_2nd frequency table
#| echo: false
ames |> 
    nominal_frequency_table(exterior_2nd)
```

## Frequency Plot

```{r}
#| label: exterior_2nd frequency plot
#| echo: false
ames |> 
    nominal_frequency_bar(exterior_2nd,
                          nominal_label = "Exterior 2nd",
                          title         = "Exterior 2nd Distribution")
```

## Relationship with Target Variable

```{r}
#| label: exterior_2nd vs sale_price
#| echo: false
ames |> 
    nominal_numeric_box(nominal       = exterior_2nd,
                        nominal_label = "Exterior 2nd",
                        numeric       = sale_price,
                        numeric_label = "Sale Price ($)",
                        title         = "Exterior 2nd vs Sale Price")
```

:::