# Data Dictionary

```{r}
#| label: variables names cleaning
#| code-fold: true
library(tidyverse)
library(AmesHousing)

ames <- ames_raw |>

    rename(id                        = Order,
           pid                       = PID,
           ms_sub_class              = `MS SubClass`,
           ms_zoning                 = `MS Zoning`,
           lot_frontage              = `Lot Frontage`,
           lot_area                  = `Lot Area`,
           street                    = Street,
           alley                     = Alley,
           lot_shape                 = `Lot Shape`,
           land_contour              = `Land Contour`,
           utilities                 = Utilities,
           lot_configuration         = `Lot Config`,
           land_slope                = `Land Slope`,
           neighborhood              = Neighborhood,
           condition_1               = `Condition 1`,
           condition_2               = `Condition 2`,
           building_type             = `Bldg Type`,
           house_style               = `House Style`,
           overall_quality           = `Overall Qual`,
           overall_condition         = `Overall Cond`,
           year_built                = `Year Built`,
           year_remod_add            = `Year Remod/Add`,
           roof_style                = `Roof Style`,
           roof_material             = `Roof Matl`,
           exterior_1st              = `Exterior 1st`,
           exterior_2nd              = `Exterior 2nd`,
           masonry_veneer_type       = `Mas Vnr Type`,
           masonry_veneer_area       = `Mas Vnr Area`,
           exterior_quality          = `Exter Qual`,
           exterior_condition        = `Exter Cond`,
           foundation                = Foundation,
           basement_quality          = `Bsmt Qual`,
           basement_condition        = `Bsmt Cond`,
           basement_exposure         = `Bsmt Exposure`,
           basement_finished_type_1  = `BsmtFin Type 1`,
           basement_area_type_1      = `BsmtFin SF 1`,
           basement_finished_type_2  = `BsmtFin Type 2`,
           basement_area_type_2      = `BsmtFin SF 2`,
           basement_unfinished_area  = `Bsmt Unf SF`,
           basement_total_area       = `Total Bsmt SF`,
           heating                   = Heating,
           heating_quality           = `Heating QC`,
           central_air               = `Central Air`,
           electrical                = Electrical,
           first_floor_area          = `1st Flr SF`,
           second_floor_area         = `2nd Flr SF`,
           low_quality_finished_area = `Low Qual Fin SF`,
           ground_living_area        = `Gr Liv Area`,
           basement_full_bathrooms   = `Bsmt Full Bath`,
           basement_half_bathrooms   = `Bsmt Half Bath`,
           full_bathrooms            = `Full Bath`,
           half_bathrooms            = `Half Bath`,
           bedroom_above_ground      = `Bedroom AbvGr`,
           kitchen_above_ground      = `Kitchen AbvGr`,
           kitchen_quality           = `Kitchen Qual`,
           total_rooms_above_ground  = `TotRms AbvGrd`,
           functional                = Functional,
           fireplaces                = Fireplaces,
           fireplace_quality         = `Fireplace Qu`,
           garage_type               = `Garage Type`,
           garage_year_built         = `Garage Yr Blt`,
           garage_finish             = `Garage Finish`,
           garage_cars               = `Garage Cars`,
           garage_area               = `Garage Area`,
           garage_quality            = `Garage Qual`,
           garage_condition          = `Garage Cond`,
           paved_drive               = `Paved Drive`,
           wood_deck_area            = `Wood Deck SF`,
           open_porch_area           = `Open Porch SF`,
           enclosed_porch_area       = `Enclosed Porch`,
           three_season_porch_area   = `3Ssn Porch`,
           screen_porch_area         = `Screen Porch`,
           pool_area                 = `Pool Area`,
           pool_quality              = `Pool QC`,
           fence                     = Fence,
           misc_feature              = `Misc Feature`,
           misc_value                = `Misc Val`,
           month_sold                = `Mo Sold`,
           year_sold                 = `Yr Sold`,
           sale_type                 = `Sale Type`,
           sale_condition            = `Sale Condition`,
           sale_price                =  SalePrice)
```

```{r}
#| echo: false
ames |> write_rds(file = "data/ames-renamed.RDS")
```



+-----------------------------+-----------+---------------------------------------------------------------------------------+
| Variable Name               | Type      | Description                                                                     |
+=============================+===========+=================================================================================+
| `id`                        | _Numeric_ | Unique observation ID                                                           |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `pid`                       | _Nominal_ | Parcel identification number - can be used with city web site for parcel review |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `ms_sub_class`              | _Nominal_ | Identifies the type of dwelling involved in the sale                            |
|                             |           |                                                                                 |
|                             |           | - One Story 1946 and Newer All Styles                                           |
|                             |           | - One Story 1945 and Older                                                      |
|                             |           | - One Story with Finished Attic All Ages                                        |
|                             |           | - One and Half Story Unfinished All Ages                                        |
|                             |           | - One and Half Story Finished All Ages                                          |
|                             |           | - Two Story 1946 and Newer                                                      |
|                             |           | - Two Story 1945 and Older                                                      |
|                             |           | - Two and Half Story All Ages                                                   |
|                             |           | - Split or Multilevel                                                           |
|                             |           | - Split Foyer                                                                   |
|                             |           | - Duplex All Styles and Ages                                                    |
|                             |           | - One Story PUD 1946 and Newer                                                  |
|                             |           | - One and Half Story PUD All Ages                                               |
|                             |           | - Two Story PUD 1946 and Newer                                                  |
|                             |           | - PUD Multilevel Split Level Foyer                                              |
|                             |           | - Two Family Conversion All Styles and Ages                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `ms_zoning`                 | _Nominal_ | Identifies the general zoning classification of the sale                        |
|                             |           |                                                                                 |
|                             |           | - Agriculture                                                                   |
|                             |           | - Commercial                                                                    |
|                             |           | - Floating Village Residential                                                  |
|                             |           | - Industrial                                                                    |
|                             |           | - Residential High Density                                                      |
|                             |           | - Residential Low Density                                                       |
|                             |           | - Residential Medium Density                                                    |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `lot_frontage`              | _Numeric_ | Linear feet of street connected to property                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `lot_area`                  | _Numeric_ | Lot size in square feet                                                         |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `street`                    | _Nominal_ | Type of road access to property                                                 |
|                             |           |                                                                                 |
|                             |           | - Gravel                                                                        |
|                             |           | - Paved                                                                         |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `alley`                     | _Nominal_ | Type of alley access to property                                                |
|                             |           |                                                                                 |
|                             |           | - Gravel                                                                        |
|                             |           | - Paved                                                                         |
|                             |           | - No Alley Access                                                               |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `lot_shape`                 | _Nominal_ | General shape of property                                                       |
|                             |           |                                                                                 |
|                             |           | - Irregular                                                                     |
|                             |           | - Moderately Irregular                                                          |
|                             |           | - Slightly Irregular                                                            |
|                             |           | - Regular                                                                       |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `land_contour`              | _Nominal_ | Flatness of the property                                                        |
|                             |           |                                                                                 |
|                             |           | - Near Flat Level                                                               |
|                             |           | - Banked                                                                        |
|                             |           | - Hillside                                                                      |
|                             |           | - Depression                                                                    |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `utilities`                 | _Nominal_ | Type of utilities available                                                     |
|                             |           |                                                                                 |
|                             |           | - Electricity Gas                                                               |
|                             |           | - Electricity Gas Water                                                         |
|                             |           | - All Public Utilities                                                          |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `lot_configuration`         | _Nominal_ | Lot configuration                                                               |
|                             |           |                                                                                 |
|                             |           | - Inside Lot                                                                    |
|                             |           | - Corner Lot                                                                    |
|                             |           | - Cul de Sac                                                                    |
|                             |           | - Frontage on 2 Sides                                                           |
|                             |           | - Frontage on 3 Sides                                                           |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `land_slope`                | _Nominal_ | Slope of property                                                               |
|                             |           |                                                                                 |
|                             |           | - Gentle Slope                                                                  |
|                             |           | - Moderate Slope                                                                |
|                             |           | - Severe Slope                                                                  |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `neighborhood`              | _Nominal_ | Physical locations within Ames city limits                                      |
|                             |           |                                                                                 |
|                             |           | - Bloomington Heights                                                           |
|                             |           | - Bluestem                                                                      |
|                             |           | - Briardale                                                                     |
|                             |           | - Brookside                                                                     |
|                             |           | - Clear Creek                                                                   |
|                             |           | - College Creek                                                                 |
|                             |           | - Crawford                                                                      |
|                             |           | - Edwards                                                                       |
|                             |           | - Gilbert                                                                       |
|                             |           | - Greens                                                                        |
|                             |           | - Green Hills                                                                   |
|                             |           | - Iowa DOT and Rail Road                                                        |
|                             |           | - Landmark                                                                      |
|                             |           | - Meadow Village                                                                |
|                             |           | - Mitchell                                                                      |
|                             |           | - North Ames                                                                    |
|                             |           | - Northridge                                                                    |
|                             |           | - Northpark Villa                                                               |
|                             |           | - Northridge Heights                                                            |
|                             |           | - Northwest Ames                                                                |
|                             |           | - Old Town                                                                      |
|                             |           | - South and West of Iowa State University                                       |
|                             |           | - Sawyer                                                                        |
|                             |           | - Sawyer West                                                                   |
|                             |           | - Somerset                                                                      |
|                             |           | - Stone Brook                                                                   |
|                             |           | - Timberland                                                                    |
|                             |           | - Veenker                                                                       |
|                             |           | - Hayden Lake                                                                   |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `condition_1`               | _Nominal_ | Proximity to various conditions                                                 |
|                             |           |                                                                                 |
|                             |           | - Adjacent Arterial Street                                                      |
|                             |           | - Adjacent Feeder Street                                                        |
|                             |           | - Normal                                                                        |
|                             |           | - Within 200 North South Railroad                                               |
|                             |           | - Adjacent North South Railroad                                                 |
|                             |           | - Near Positive off Site Feature                                                |
|                             |           | - Adjacent Postive off Site Feature                                             |
|                             |           | - Within 200 East West Railroad                                                 |
|                             |           | - Adjacent East West Railroad                                                   |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `condition_2`               | _Nominal_ | Proximity to various conditions (if more than one is present)                   |
|                             |           |                                                                                 |
|                             |           | - Adjacent Arterial Street                                                      |
|                             |           | - Adjacent Feeder Street                                                        |
|                             |           | - Normal                                                                        |
|                             |           | - Within 200 North South Railroad                                               |
|                             |           | - Adjacent North South Railroad                                                 |
|                             |           | - Near Positive off Site Feature                                                |
|                             |           | - Adjacent Postive off Site Feature                                             |
|                             |           | - Within 200 East West Railroad                                                 |
|                             |           | - Adjacent East West Railroad                                                   |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `building_type`             | _Nominal_ | Type of dwelling                                                                |
|                             |           |                                                                                 |
|                             |           | - One Family Detached                                                           |
|                             |           | - Two Family Conversion                                                         |
|                             |           | - Duplex                                                                        |
|                             |           | - Townhouse End Unit                                                            |
|                             |           | - Townhouse Inside Unit                                                         |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `house_style`               | _Nominal_ | Style of dwelling                                                               |
|                             |           |                                                                                 |
|                             |           | - One Story                                                                     |
|                             |           | - One and Half Story 2nd Level Finished                                         |
|                             |           | - One and Half Story 2nd Level Unfinished                                       |
|                             |           | - Two Story                                                                     |
|                             |           | - Two and Half Story 2nd Level Finished                                         |
|                             |           | - Two and Half Story 2nd Level Unfinished                                       |
|                             |           | - Split Foyer                                                                   |
|                             |           | - Split Level                                                                   |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `overall_quality`           | _Nominal_ | Rates the overall material and finish of the house                              |
|                             |           |                                                                                 |
|                             |           | - Very Poor                                                                     |
|                             |           | - Poor                                                                          |
|                             |           | - Fair                                                                          |
|                             |           | - Below Average                                                                 |
|                             |           | - Average                                                                       |
|                             |           | - Above Average                                                                 |
|                             |           | - Good                                                                          |
|                             |           | - Very Good                                                                     |
|                             |           | - Excellent                                                                     |
|                             |           | - Very Excellent                                                                |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `overall_condition`         | _Nominal_ | Rates the overall condition of the house                                        |
|                             |           |                                                                                 |
|                             |           | - Very Poor                                                                     |
|                             |           | - Poor                                                                          |
|                             |           | - Fair                                                                          |
|                             |           | - Below Average                                                                 |
|                             |           | - Average                                                                       |
|                             |           | - Above Average                                                                 |
|                             |           | - Good                                                                          |
|                             |           | - Very Good                                                                     |
|                             |           | - Excellent                                                                     |
|                             |           | - Very Excellent                                                                |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `year_built`                | _Numeric_ | Original construction date                                                      |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `year_remod_add`            | _Numeric_ | Remodel date (same as construction date if no remodeling or additions)          |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `roof_style`                | _Nominal_ | Type of roof                                                                    |
|                             |           |                                                                                 |
|                             |           | - Flat                                                                          |
|                             |           | - Gable                                                                         |
|                             |           | - Gabrel Barn                                                                   |
|                             |           | - Hip                                                                           |
|                             |           | - Mansard                                                                       |
|                             |           | - Shed                                                                          |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `roof_material`             | _Nominal_ | Roof material                                                                   |
|                             |           |                                                                                 |
|                             |           | - Clay or Tile                                                                  |
|                             |           | - Composite Shingle                                                             |
|                             |           | - Membrane                                                                      |
|                             |           | - Metal                                                                         |
|                             |           | - Roll                                                                          |
|                             |           | - Gravel and Tar                                                                |
|                             |           | - Wood Shakes                                                                   |
|                             |           | - Wood Shingles                                                                 |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `exterior_1st`              | _Nominal_ | Exterior covering on house                                                      |
|                             |           |                                                                                 |
|                             |           | - Asbestos Shingles                                                             |
|                             |           | - Asphalt Shingles                                                              |
|                             |           | - Brick Common                                                                  |
|                             |           | - Brick Face                                                                    |
|                             |           | - Cinder Block                                                                  |
|                             |           | - Cement Board                                                                  |
|                             |           | - Hard Board                                                                    |
|                             |           | - Imitation Stucco                                                              |
|                             |           | - Metal Siding                                                                  |
|                             |           | - Other                                                                         |
|                             |           | - Plywood                                                                       |
|                             |           | - PreCast                                                                       |
|                             |           | - Stone                                                                         |
|                             |           | - Stucco                                                                        |
|                             |           | - Vinyl Siding                                                                  |
|                             |           | - Wood Siding                                                                   |
|                             |           | - Wood Shingles                                                                 |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `exterior_2nd`              | _Nominal_ | Exterior covering on house (if more than one material)                          |
|                             |           |                                                                                 |
|                             |           | - Asbestos Shingles                                                             |
|                             |           | - Asphalt Shingles                                                              |
|                             |           | - Brick Common                                                                  |
|                             |           | - Brick Face                                                                    |
|                             |           | - Cinder Block                                                                  |
|                             |           | - Cement Board                                                                  |
|                             |           | - Hard Board                                                                    |
|                             |           | - Imitation Stucco                                                              |
|                             |           | - Metal Siding                                                                  |
|                             |           | - Other                                                                         |
|                             |           | - Plywood                                                                       |
|                             |           | - PreCast                                                                       |
|                             |           | - Stone                                                                         |
|                             |           | - Stucco                                                                        |
|                             |           | - Vinyl Siding                                                                  |
|                             |           | - Wood Siding                                                                   |
|                             |           | - Wood Shingles                                                                 |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `masonry_veneer_type`       | _Nominal_ | Masonry veneer type                                                             |
|                             |           |                                                                                 |
|                             |           | - Brick Common                                                                  |
|                             |           | - Brick Face                                                                    |
|                             |           | - Cinder Block                                                                  |
|                             |           | - None                                                                          |
|                             |           | - Stone                                                                         |
|                             |           | - None                                                                          |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `masonry_veneer_area`       | _Numeric_ | Masonry veneer area in square feet                                              |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `exterior_quality`          | _Nominal_ | Evaluates the quality of the material on the exterior                           |
|                             |           |                                                                                 |
|                             |           | - Poor                                                                          |
|                             |           | - Fair                                                                          |
|                             |           | - Average Typical                                                               |
|                             |           | - Good                                                                          |
|                             |           | - Excellent                                                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `exterior_condition`        | _Nominal_ | Evaluates the present condition of the material on the exterior                 |
|                             |           |                                                                                 |
|                             |           | - Poor                                                                          |
|                             |           | - Fair                                                                          |
|                             |           | - Average Typical                                                               |
|                             |           | - Good                                                                          |
|                             |           | - Excellent                                                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `foundation`                | _Nominal_ | Evaluates the present condition of the material on the exterior                 |
|                             |           |                                                                                 |
|                             |           | - Brick and Tile                                                                |
|                             |           | - Cinder Block                                                                  |
|                             |           | - Poured Contrete                                                               |
|                             |           | - Slab                                                                          |
|                             |           | - Stone                                                                         |
|                             |           | - Wood                                                                          |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `basement_quality`          | _Nominal_ | Evaluates the height of the basement                                            |
|                             |           |                                                                                 |
|                             |           | - No Basement                                                                   |
|                             |           | - Poor                                                                          |
|                             |           | - Fair                                                                          |
|                             |           | - Average Typical                                                               |
|                             |           | - Good                                                                          |
|                             |           | - Excellent                                                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `basement_condition`        | _Nominal_ | Evaluates the general condition of the basement                                 |
|                             |           |                                                                                 |
|                             |           | - No Basement                                                                   |
|                             |           | - Poor                                                                          |
|                             |           | - Fair                                                                          |
|                             |           | - Average Typical                                                               |
|                             |           | - Good                                                                          |
|                             |           | - Excellent                                                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `basement_exposure`         | _Nominal_ | Refers to walkout or garden level walls                                         |
|                             |           |                                                                                 |
|                             |           | - No Basement                                                                   |
|                             |           | - No Exposure                                                                   |
|                             |           | - Minimum Exposure                                                              |
|                             |           | - Average Exposure                                                              |
|                             |           | - Good Exposure                                                                 |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `basement_finished_type_1`  | _Nominal_ | Rating of basement finished area                                                |
|                             |           |                                                                                 |
|                             |           | - No Basement                                                                   |
|                             |           | - Unfinshed                                                                     |
|                             |           | - Low Quality                                                                   |
|                             |           | - Average Rec Room                                                              |
|                             |           | - Below Average Living Quarters                                                 |
|                             |           | - Average Living Quarters                                                       |
|                             |           | - Good Living Quarters                                                          |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `basement_area_type_1`      | _Numeric_ | Type 1 finished square feet                                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `basement_finished_type_2`  | _Nominal_ | Rating of basement finished area (if multiple types)                            |
|                             |           |                                                                                 |
|                             |           | - No Basement                                                                   |
|                             |           | - Unfinshed                                                                     |
|                             |           | - Low Quality                                                                   |
|                             |           | - Average Rec Room                                                              |
|                             |           | - Below Average Living Quarters                                                 |
|                             |           | - Average Living Quarters                                                       |
|                             |           | - Good Living Quarters                                                          |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `basement_area_type_2`      | _Numeric_ | Type 2 finished square feet                                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `basement_unfinished_area`  | _Numeric_ | Unfinished square feet of basement area                                         |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `basement_total_area`       | _Numeric_ | Total square feet of basement area                                              |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `heating`                   | _Nominal_ | Type of heating                                                                 |
|                             |           |                                                                                 |
|                             |           | - Floor Furnace                                                                 |
|                             |           | - Gas Forced Warm Air Furnace                                                   |
|                             |           | - Gas Hot Water or Steam Heat                                                   |
|                             |           | - Gravity Furnace                                                               |
|                             |           | - Hot Water or Steam Heat other than Gas                                        |
|                             |           | - Average Living Quarters                                                       |
|                             |           | - Wall Furnace                                                                  |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `heating_quality`           | _Nominal_ | Heating quality and condition                                                   |
|                             |           |                                                                                 |
|                             |           | - Poor                                                                          |
|                             |           | - Fair                                                                          |
|                             |           | - Average Typical                                                               |
|                             |           | - Good                                                                          |
|                             |           | - Excellent                                                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `central_air`               | _Nominal_ | Heating quality and condition                                                   |
|                             |           |                                                                                 |
|                             |           | - No                                                                            |
|                             |           | - Yes                                                                           |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `electrical`                | _Nominal_ | Heating quality and condition                                                   |
|                             |           |                                                                                 |
|                             |           | - Mixed                                                                         |
|                             |           | - Fuse Box Poor                                                                 |
|                             |           | - Fuse Box Fair                                                                 |
|                             |           | - Fuse Box Average                                                              |
|                             |           | - Standard Circuit Breakers and Romex                                           |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `first_floor_area`          | _Numeric_ | First Floor square feet                                                         |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `second_floor_area`         | _Numeric_ | Second floor square feet                                                        |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `low_quality_finished_area` | _Numeric_ | Low quality finished square feet (all floors)                                   |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `ground_living_area`        | _Numeric_ | Above grade (ground) living area square feet                                    |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `basement_full_bathrooms`   | _Numeric_ | Basement full bathrooms                                                         |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `basement_half_bathrooms`   | _Numeric_ | Basement half bathrooms                                                         |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `full_bathrooms`            | _Numeric_ | Full bathrooms above grade                                                      |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `half_bathrooms`            | _Numeric_ | Half baths above grade                                                          |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `bedroom_above_ground`      | _Numeric_ | Bedrooms above grade (does NOT include basement bedrooms)                       |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `kitchen_above_ground`      | _Numeric_ | Kitchens above grade                                                            |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `kitchen_quality`           | _Nominal_ | Kitchen quality                                                                 |
|                             |           |                                                                                 |
|                             |           | - Poor                                                                          |
|                             |           | - Fair                                                                          |
|                             |           | - Average Typical                                                               |
|                             |           | - Good                                                                          |
|                             |           | - Excellent                                                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `total_rooms_above_ground`  | _Numeric_ | Total rooms above grade (does not include bathrooms)                            |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `functional`                | _Nominal_ | Home functionality (Assume typical unless deductions are warranted)             |
|                             |           |                                                                                 |
|                             |           | - Salvage Only                                                                  |
|                             |           | - Severely Damaged                                                              |
|                             |           | - Major Deductions 2                                                            |
|                             |           | - Major Deductions 1                                                            |
|                             |           | - Moderate Deductions                                                           |
|                             |           | - Minor Deductions 2                                                            |
|                             |           | - Minor Deductions 1                                                            |
|                             |           | - Typical Functionality                                                         |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `fireplaces`                | _Numeric_ | Number of fireplaces                                                            |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `fireplace_quality`         | _Nominal_ | Fireplace quality                                                               |
|                             |           |                                                                                 |
|                             |           | - No Fireplace                                                                  |
|                             |           | - Poor                                                                          |
|                             |           | - Fair                                                                          |
|                             |           | - Average Typical                                                               |
|                             |           | - Good                                                                          |
|                             |           | - Excellent                                                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `garage_type`               | _Nominal_ | Garage location                                                                 |
|                             |           |                                                                                 |
|                             |           | - More than One Type                                                            |
|                             |           | - Attached to Home                                                              |
|                             |           | - Basement Garage                                                               |
|                             |           | - Built-In                                                                      |
|                             |           | - Car Port                                                                      |
|                             |           | - Detached from Home                                                            |
|                             |           | - No Garage                                                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `garage_year_built`         | _Numeric_ | Year garage was built                                                           |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `garage_finish`             | _Nominal_ | Interior finish of the garage                                                   |
|                             |           |                                                                                 |
|                             |           | - No Garage                                                                     |
|                             |           | - Finished                                                                      |
|                             |           | - Rough Finished                                                                |
|                             |           | - Unfinished                                                                    |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `garage_cars`               | _Numeric_ | Size of garage in car capacity                                                  |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `garage_area`               | _Numeric_ | Size of garage in square feet                                                   |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `garage_quality`            | _Nominal_ | Garage quality                                                                  |
|                             |           |                                                                                 |
|                             |           | - No Garage                                                                     |
|                             |           | - Poor                                                                          |
|                             |           | - Fair                                                                          |
|                             |           | - Average Typical                                                               |
|                             |           | - Good                                                                          |
|                             |           | - Excellent                                                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `garage_condition`          | _Nominal_ | Garage condition                                                                |
|                             |           |                                                                                 |
|                             |           | - No Garage                                                                     |
|                             |           | - Poor                                                                          |
|                             |           | - Fair                                                                          |
|                             |           | - Average Typical                                                               |
|                             |           | - Good                                                                          |
|                             |           | - Excellent                                                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `paved_drive`               | _Nominal_ | Garage condition                                                                |
|                             |           |                                                                                 |
|                             |           | - Paved                                                                         |
|                             |           | - Partial Pavement                                                              |
|                             |           | - Dirt Gravel                                                                   |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `wood_deck_area`            | _Numeric_ | Wood deck area in square feet                                                   |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `open_porch_area`           | _Numeric_ | Open porch area in square feet                                                  |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `enclosed_porch_area`       | _Numeric_ | Enclosed porch area in square feet                                              |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `three_season_porch_area`   | _Numeric_ | Three season porch area in square feet                                          |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `screen_porch_area`         | _Numeric_ | Screen porch area in square feet                                                |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `pool_area`                 | _Numeric_ | Pool area in square feet                                                        |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `pool_quality`              | _Nominal_ | Pool quality                                                                    |
|                             |           |                                                                                 |
|                             |           | - No Pool                                                                       |
|                             |           | - Fair                                                                          |
|                             |           | - Average Typical                                                               |
|                             |           | - Good                                                                          |
|                             |           | - Excellent                                                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `fence`                     | _Nominal_ | Fence quality                                                                   |
|                             |           |                                                                                 |
|                             |           | - No Fence                                                                      |
|                             |           | - Minimum Wood Wire                                                             |
|                             |           | - Good Wood                                                                     |
|                             |           | - Minimum Privacy                                                               |
|                             |           | - Good Privacy                                                                  |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `misc_feature`              | _Nominal_ | Miscellaneous feature not covered in other categories                           |
|                             |           |                                                                                 |
|                             |           | - Elevator                                                                      |
|                             |           | - Second Garage if not Described in Garage Section                              |
|                             |           | - Other                                                                         |
|                             |           | - Shed over 100 SF                                                              |
|                             |           | - Tennis Court                                                                  |
|                             |           | - None                                                                          |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `misc_value`                | _Numeric_ | Value of miscellaneous feature ($)                                              |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `month_sold`                | _Numeric_ | Month Sold                                                                      |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `year_sold`                 | _Numeric_ | Year Sold                                                                       |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `sale_type`                 | _Nominal_ | Type of sale                                                                    |
|                             |           |                                                                                 |
|                             |           | - Warranty Deed Conventional                                                    |
|                             |           | - Warranty Deed Cash                                                            |
|                             |           | - Warranty Deed VA Loan                                                         |
|                             |           | - Home just Constructed and Sold                                                |
|                             |           | - Court Officer Deed Estate                                                     |
|                             |           | - Contract 15 Down Payment Regular Terms                                        |
|                             |           | - Contract Low Down Payment and Low Interest                                    |
|                             |           | - Contract Low Interest                                                         |
|                             |           | - Contract Low Down                                                             |
|                             |           | - Other                                                                         |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `sale_condition`            | _Nominal_ | Type of sale                                                                    |
|                             |           |                                                                                 |
|                             |           | - Normal Sale                                                                   |
|                             |           | - Abnormal Sale                                                                 |
|                             |           | - Adjoining Land Purchase                                                       |
|                             |           | - Allocation                                                                    |
|                             |           | - Sale between Family Members                                                   |
|                             |           | - Home was not Completed when Last Assessed                                     |
+-----------------------------+-----------+---------------------------------------------------------------------------------+
| `sale_price`                | _Numeric_ | Sale price ($)                                                                  |
+-----------------------------+-----------+---------------------------------------------------------------------------------+