# Target Variable

::: {.callout-note appearance="simple"}
## Main Findings

- The target variable `sale_price` has no missing values and looks skewed to the
right

- A logartihmic distribution solves well the skewness of the distribution

:::

## Distribution

```{r}
#| echo: false
source(file = "functions/stats.R")
source(file = "functions/plots.R")

ames <- read_rds(file = "data/ames-renamed.RDS")
```

```{r}
#| echo: false
ames |> 
  numeric_distribution(sale_price,
                       xlabel = "Sale Price ($)",
                       title  = "Sale Price Distribution")
```

## Numerical Summaries

```{r}
#| echo: false
ames |>
  numeric_summary_table(sale_price)
```

## Box-Cox transformation

The following calculation suggests that a logarithm transformation should be
applied to reduce skewness.

[Reference](https://r-coder.com/box-cox-transformation-r/)

```{r}
b <- MASS::boxcox(lm(sale_price ~ 1, data = ames), plotit = FALSE)

# Exact lambda
b$x[which.max(b$y)]
```

Observe that after the logarithmic transformation there is still evidence that
the variable is not normally distributed:

```{r}
ames |> 
  mutate(sale_price = log10(sale_price)) |> 
  pull() |> 
  shapiro.test()
```

As the p-value is lower than `1%` level of significance we have evidence to
reject the null hypothesis of normality.

## Distribution after log10 Transformation

```{r}
#| echo: false
ames |> 
  numeric_distribution(log10(sale_price),
                       xlabel = "log10(Sale Price ($))",
                       title  = "Sale Price Distribution")
```

## Numerical Summaries after log10 Transformation

```{r}
#| echo: false
ames |>
  numeric_summary_table(log10(sale_price))
```
